Using GLS and Estimating the Covariance Matrix

### 2024-02-07 src/explore/20240202-estcovmat.qmd
Finished CSSM presentation.

---
title: "Estimating the Covariance Matrix"
author:
  - name: Caleb Leedy
date: today
date-format: "D MMMM YYYY"
format:
  pdf:
    include-in-header: 
      - "latex_header.tex"
---

>>>>

---
title: "Using GLS and Estimating the Covariance Matrix"
author:
  - name: Caleb Leedy
date: today
date-format: "D MMMM YYYY"
format:
  pdf:
    include-in-header: 
      - "latex_header.tex"
---
